---
title: "p8105_hw5_SL5454"
author: "Sining Leng"
date: "2024-11-07"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(broom)
library(purrr)
library(ggplot2)
```

## Problem 1
```{r}
bday = function(n) {

  bdays = sample(1:365, size = n, replace = TRUE)
  
  duplicate = length(unique(bdays)) < n

  return(duplicate)
  
}

bday_samp = 
  expand_grid(
    n = 2:50,
    iter = 1:10000
  ) |> 
  mutate(res = map_lgl(n, bday)) |> 
  group_by(n) |> 
  summarize(prob = mean(res))

bday_samp |>
  ggplot(aes(x = n, y = prob)) + 
  geom_line()
```

The probability that at least two people in the group will share a birthday increasing with group size. Around group size of 23, the probability exceeds 50%.


## Problem 2

```{r}
t_test = function(n = 30, sigma = 5, mu) {
  
  data = rnorm(n, mean = mu, sd = sigma)
  
  ttest_result = t.test(data, mu = 0, conf.level = 0.95) |>
    broom::tidy()
  
  return(ttest_result)
}

set.seed(123)
mu_df = 
  expand_grid(
    mu = 0:6,
    iter = 1:5000
  ) |>
  mutate(output = map(mu, ~t_test(mu = .x))) |>
  unnest(output)

```

Repeat mu = 0:6
```{r}
rejected =
  mu_df |>
  group_by(mu) |>
  summarize(
    power = mean(p.value < 0.05),
    avg_est = mean(estimate),
    avg_reject = mean(estimate[p.value < 0.05])
  )
```

### Plot 2.1
```{r}
rejected |>
  ggplot(aes(x = mu, y = power)) +
  geom_line() +
  labs(title = "Power of t-test vs. True Value of mu",
       x = "mu",
       y = "Power") +
  theme_minimal()
```

The plot shows that the greater the effective size the larger the power of this t test.

### Plot 2.2
```{r}
rejected |>
  ggplot(aes(x = mu, y = avg_est)) +
  geom_point() +
  geom_line() + 
  labs(title = "Average Estimate vs. True Value",
       x = "True Value of mu",
       y = "Average Estimate of mu")

rejected |>
  ggplot(aes(x = mu, y = avg_reject)) +
  geom_point() +
  geom_line() +
  labs(title = "Average Estimate in Rejected vs. True Value",
       x = "True Value of mu",
       y = "Average Estimate of mu with Rejected Null")
``` 
  
The estimates for samples where the null was rejected tend to be higher than the true μ, especially for smaller effect sizes. Thus, the sample average of 𝜇̂ across tests for which the null is rejected approximately equal to the true value of μ, but the sample mean 𝜇̂ differs from the true value μ when μ < 4.


## Problem 3

```{r}
us_homicide = 
  read_csv("./data/homicide-data.csv") |>
  janitor::clean_names()

```

There are 12 variables in the raw dataset. It contains status and location of homicides reported from 2010 to 2016. It also includes variables that describe basic information of victims, such as name, sex and age.

```{r}
count_homicide =
  us_homicide |>
  mutate(
    state = if_else(city == "Tulsa" & state == "AL", "OK", state),
    city_state = paste(city, state, sep = ",")
  ) |>
  group_by(city_state) |>
  summarize(
    total_homicides = n(),
    unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))
  ) |>
  ungroup()

count_homicide
```

### Baltimore, MD
```{r}
baltimore = 
  count_homicide |>
  filter(city_state == "Baltimore,MD") 

baltimore_prop =
  prop.test(
    x = baltimore$unsolved_homicides,
    n = baltimore$total_homicides
  ) |>
  broom::tidy() 

baltimore_est =
  baltimore_prop|>
  select(estimate, conf.low, conf.high)

baltimore_est
```

### Every city
```{r}
city_homicide = 
  count_homicide |>
  mutate(
    test_result = map2(
      unsolved_homicides,
      total_homicides,
      ~ prop.test(x = .x, n = .y)
    )
  ) |>
  mutate(
    test_result = map(test_result, broom::tidy)
  ) |>
  unnest(test_result) |>
  select(city_state, estimate, conf.low, conf.high)

city_homicide
```

### Plot 3
```{r}
city_homicide |>
  mutate(city_state = fct_reorder(city_state, estimate)) |>
  ggplot(aes(x = estimate, y = city_state)) +
  geom_point() +
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high)) +
  labs(
    title = "Proportion of Unsolved Homicides in Each City",
    x = "Proportion of Unsolved Homicides",
    y = "City"
  ) +
  theme_minimal()

```

